\gettitle

### 2019-12-01 assignment3/submission3.tex
Solution to Exercise 3.1a2
Add solution to exercise 4

\begin{figure}[ht!]
\begin{tikzpicture}[scale=0.15]
\foreach \x in {1,...,97} {
	\draw (\x,0) -- (\x, 2);
	\draw (\x, -5) -- (\x, -7);
};
\draw (0,0) -- (97,0);
\draw (0,-5) -- (97,-5);
\node at(0, -1) {\tiny Master};
\node at(0, -4) {\tiny Slave};
\foreach \x/\n in {3/7,9/8,15/9,21/10,27/11,33/12,39/13,45/14,51/15,57/16,63/17,69/18,75/19,81/20,87/21,93/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,1) (a\n) {}
		node[below=7mm, above of=a\n] {\tiny \n};
};
\foreach \x/\n in {3/3,9/4,15/5,21/6,27/7,33/8,37/9,41/10,45/11,49/12,53/13,57/14,61/15,65/16,69/17,73/18,77/19,81/20,87/21,93/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,-6) (b\n) {}
		node[above=7mm, below of=b\n] {\tiny \n};
};
\path[draw,->] 
	(b5.north) edge (a10.south)
	(a11.south) edge (b8.north);
\end{tikzpicture}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((10 - 5) - (8 - 11)) = \frac12(5 + 3) = 4  &\\
d = 1 & \\
\Delta = 12, C_s(t_4 + \Delta) = 20 & \\
\frac{dC_S}{dt} = \frac{12 + 4}{12} = \frac{4}{3} &
\end{align*}

@@

@@

>>>>

\begin{figure}[ht!]
\begin{tikzpicture}[scale=0.15]
\foreach \x in {1,...,97} {
	\draw (\x,0) -- (\x, 2);
	\draw (\x, -5) -- (\x, -7);
};
\draw (0,0) -- (97,0);
\draw (0,-5) -- (97,-5);
\node at(0, -1) {\tiny Master};
\node at(0, -4) {\tiny Slave};
\foreach \x/\n in {3/7,9/8,15/9,21/10,27/11,33/12,39/13,45/14,51/15,57/16,63/17,69/18,75/19,81/20,87/21,93/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,1) (a\n) {}
		node[below=7mm, above of=a\n] {\tiny \n};
};
\foreach \x/\n in {3/3,9/4,15/5,21/6,27/7,33/8,37/9,41/10,45/11,49/12,53/13,57/14,61/15,65/16,69/17,73/18,77/19,81/20,87/21,93/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,-6) (b\n) {}
		node[above=7mm, below of=b\n] {\tiny \n};
};
\path[draw,->] 
	(b5.north) edge (a10.south)
	(a11.south) edge (b8.north);
\end{tikzpicture}
\caption{Solution for Figure 1}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((10 - 5) - (8 - 11)) = \frac12(5 + 3) = 4  &\\
d = 1 & \\
\Delta = 12, C_s(t_4 + \Delta) = 20 & \\
\frac{dC_S}{dt} = \frac{12 + 4}{12} = \frac{4}{3} &
\end{align*}

\begin{figure}[ht!]
	\begin{tikzpicture}[scale=0.15]
	\foreach \x in {1,...,97} {
		\draw (\x,0) -- (\x, 2);
		\draw (\x, -5) -- (\x, -7);
	};
	\draw (0,0) -- (97,0);
	\draw (0,-5) -- (97,-5);
	\node at(0, -1) {\tiny Master};
	\node at(0, -4) {\tiny Slave};
	\foreach \x/\n in {3/1,9/2,15/3,21/4,27/5,33/6,39/7,45/8,51/9,57/10,63/11,69/12,75/13,81/14,87/15,93/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,1) (a\n) {}
			node[below=7mm, above of=a\n] {\tiny \n};
	};
	\foreach \x/\n in {3/6,9/7,15/8,21/9,27/10,33/11,49/12,65/13,81/14,87/15,93/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,-6) (b\n) {}
			node[above=7mm, below of=b\n] {\tiny \n};
	};
	\path[draw,->]
		(b8.north) edge (a4.south)
		(a5.south) edge (b11.north);
\end{tikzpicture}
\caption{Solution for Figure 2}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((4 - 8) - (11 - 5)) = \frac12(-4 - 6) = -5  &\\
d = 1 & \\
\Delta = 3, C_s(t_4 + \Delta) = 14 & \\
\frac{dC_S}{dt} = \frac{3}{3 +5} = \frac{3}{8} &
\end{align*}

@@

See Figure 4

\begin{figure}[!ht]
    \centering
    \begin{tikzpicture}[auto,node distance=1.5cm,event/.style={fill=black,circle, inner sep=0pt, minimum size=5pt},state/.style={draw,rectangle, red, color=red, inner sep=0pt, minimum size=5pt, minimum width=10pt}, msg/.style={-latex,thick}, marker/.style={-latex,thick,red}]
        \node[] (p1s) {\(P_1\)};
        \node[] (p2s) [below = of p1s] {\(P_2\)};
        \node[] (p3s) [below = of p2s] {\(P_3\)};

        \node[] (p1e) [right = 13cm of p1s] {};
        \node[] (p2e) [right = 13cm of p2s] {};
        \node[] (p3e) [right = 13cm of p3s] {};

        \path (p1s.east) edge (p1e);
        \path (p2s.east) edge (p2e);
        \path (p3s.east) edge (p3e);

        \node[event,label={\(e_1^1\)}] (e11) [right = 1.3cm of p1s] {};
        \node[event,label={\(e_2^1\)}] (e21) [right = 1cm of p2s] {};
        \node[event,label={\(e_3^1\)}] (e31) [right = 2cm of p3s] {};

        \node[event,label={\(e_1^2\)}] (e12) [right = 4.2cm of p1s] {};
        \node[event,label={\(e_2^2\)}] (e22) [right = 2.1cm of p2s] {};
        \node[event,label={\(e_3^2\)}] (e32) [right = 4cm of p3s] {};

        \node[event,label={\(e_1^3\)}] (e13) [right = 6cm of p1s] {};
        \node[event,label={\(e_2^3\)}] (e23) [right = 4.5cm of p2s] {};
        \node[event,label={\(e_3^3\)}] (e33) [right = 10cm of p3s] {};

        \node[event,label={\(e_1^4\)}] (e14) [right = 7cm of p1s] {};
        \node[event,label=below:{\(e_2^4\)}] (e24) [right = 8.5cm of p2s] {};

        \node[event,label={\(e_1^5\)}] (e15) [right = 10.5cm of p1s] {};
        \node[event,label={\(e_2^5\)}] (e25) [right = 9cm of p2s] {};

        \node[event,label={\(e_2^6\)}] (e26) [right = 12.5cm of p2s] {};

        \path (e21) edge[msg] node {\(m_1\)} (e31);
        \path (e11) edge[msg] node[left] {\(m_2\)} (e23);
        \path (e22) edge[msg] node[right] {\(m_3\)} (e12);
        \path (e32) edge[msg] node[below right] {\(m_4\)} (e14);
        \path (e13) edge[msg] node[right] {\(m_5\)} (e25);
        \path (e15) edge[msg] node {\(m_6\)} (e26);
        \path (e24) edge[msg] node {\(m_7\)} (e33);

        \node[state,label={[red]:{\(s_3\)}}] (s3) [right = 3cm of p3s] {};
        \node[state,label={[red]:{\(s_1,c_4\)}}] (s1) [right = 5cm of p1s] {};
        \node[state,label={[red]below:{\(s_2,c_1\)}}] (s2) [right = 6.5cm of p2s] {};

        \node[state,label={[red]:{\(c_2\)}}] (c2) [right = 8cm of p1s] {};
        \node[state,label={[red]:{\(c_3\)}}] (c3) [right = 8.5cm of p3s] {};

        \path (s3.north east) edge[marker] node[below] {\(M\)} (s1.south west);
        \path (s1.south east) edge[marker] node[left] {\(M'\)} (s2.north west);
        \path (s2.north east) edge[marker] node[below left] {\(M''\)} (c2.south west);
        \path (s2.south east) edge[marker] node[] {\(M''\)} (c3.north west);
    \end{tikzpicture}

    The red boxes represent where a process saves some state. A process state save is denoted by \(s_i\) and a channel state save by \(c_j\) where \(i\) is the process number and \(j\) is the channel number.
    \caption{solution for 4.a)}
\end{figure}

@@

No channel received a message between the process starting recording and the first/second marker arriving. All channel states are empty sets.

\begin{align*}
    c_1 &= \{\}\\
    c_2 &= \{\}\\
    c_3 &= \{\}\\
    c_4 &= \{\}\\
\end{align*}
